Congestion-Aware Join Optimization in Key-Value Stores

### 2014-08-01 paper/paper.tex
Expand on related work

>>>>

There has also been some work in exploiting software-defined networking for big data applications.
Wang et al.~\cite{Wang2012} examined network traffic patterns in a Hadoop cluster and identified opportunities to combine network-aware job scheduling with dynamic routing configuration to improve job completion time.
Xiong et al.~\cite{Xiong2014} examine the usefulness of software-defined networking in supporting distributed analytical queries.
Their workload consits of read-only SQL queries where query processing is bandwidth-intensive.
They construct a global query optimizer which decides on join order and how query results should be passed between sites.
This work takes a similar approach to ours, but also identifies many opportunities for further work.
